MWA tied-array processing III: Microsecond time resolution via a synthesis filter

### 2019-10-17 ipfb.tex
Fixed up a few issues with the bibliography.

PFBs are a type of analysis filter, designed to extract spectral information out of discrete time series data.
They can be considered a generalisation of the more familiar Discrete Fourier Transform (DFT), and are designed to overcome the dual problems of uneven frequency response and spectral leakage inherent in the application of DFTs to finite length data sets.
They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
Therefore, only a brief review of the salient features are given below, in order to lay out the notation used in this paper and to prepare the reader for what follows.

\subsection{General review and mathematical description}

>>>>

PFBs are a type of analysis filter, designed to extract spectral information out of discrete time series data.
They can be considered a generalisation of the more familiar discrete Fourier transform (DFT), and are designed to overcome the dual problems of uneven frequency response and spectral leakage inherent in the application of DFTs to data sets of finite length.
They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
Therefore, only a brief review of the salient features are given below, in order to lay out the notation used in this paper and to prepare the reader for what follows.

\subsection{General review and mathematical notation}

Like the DFT, the PFB is a transformation from the time domain, $x[m]$, to the frequency domain $X[k]$, where the $[\cdot]$ notation denotes a discretised index, and where $m$ and $k$ are indices for time and frequency, respectively.
